---
title: "GLM with different regulation methods"
author: "YUANXU"
date: "10/23/2020"
output: html_document
---
## Using the College build in ISLR
```{r}
library(glmnet)
library(ISLR) 
attach(College) 
dim(College)
```
##Randomly split the data into training set and test set each of them with 50% of origianl data
```{r}
set.seed(1) 
College=na.omit(College)
subset = sample(nrow(College),nrow(College)/2)
train.college = College[subset,]
test.college = College[-subset,]
dim(test.college)
```
##Fit a linear model using MSE method on training set, make prediction based on this model and report the test error
```{r}
fit.lm = lm(Apps~.,data=train.college)
summary(fit.lm)
```
```{r}
pred.lm = predict(fit.lm,test.college)
testerror = mean((pred.lm-test.college$Apps)**2)
testerror
```
## Fit a ridge regression model on the training set, with the lambda chosen by cross-validation.
```{r}
train.mat = model.matrix(Apps~.,data=train.college)[,-1]
test.mat = model.matrix(Apps~.,data=test.college)[,-1]
## build a sequnce of number from 10^10 to 10^-2 and use cross validation(defualt 10 k) to decide lambda
grid = 10^seq(10,-2,length=100)
ridge.mod = glmnet(train.mat,train.college$Apps,alpha = 0,lambda =grid,thresh = 1e-12)
ridge.cv = cv.glmnet(train.mat,train.college$Apps,alpha=0)
plot(ridge.cv)
```
##predict the result with this new model and find the new MSE
```{R}
ridge.pred = predict(ridge.mod,s=ridge.cv$lambda.min,x=train.mat,y=train.college$Apps,newx = test.mat,exact=TRUE)
summary(ridge.pred)
mean((ridge.pred-test.college$Apps)**2)
```
## Using LASSO model to predict the LASSO.pred and find the new MSE.
```{R}
lass.mod = glmnet(train.mat,train.college$Apps,alpha = 1,lambda = grid,thresh = 1e-12)
lass.cv = cv.glmnet(train.mat,train.college$Apps,alpha = 1)
plot(lass.cv)
```
```{r}
lass.pred = predict(lass.mod,s=lass.cv$lambda.min,x=train.mat,y=train.college$Apps,newx = test.mat,exact = TRUE)
summary(ridge.pred)
mean((lass.pred-test.college$Apps)**2)
```
