---
title: "Logistic Regression, LDA & QDA"
author: "YUANXU"
date: "10/26/2020"
output: html_document
---
## Logistic Regreesion using Smarket data
```{r}
library(ISLR)
attach(Smarket)
df = na.omit(Smartket)
head(df)
```
```{r}
## Split data into two parts randomly cause the data is ranged by year and year also impact the Direction 
set.seed(271)
subset = sample(nrow(df),nrow(df)/3)
train_set = df[-subset,]
test_set = df[subset,]
dim(test_set)
```
```{r}
## The family = binomial indicates build logistic regression 
df.glm = glm(Direction~.,data = train_set,family = binomial)
summary(df.glm)
```
```{r}
## Using confusing matrix and test error to the predict results
df.prob = predict(df.glm,test_set,type="response")
df.pred = rep("Up",416)
df.pred[df.prob<0.5]="Down"
table(df.pred,test_set$Direction)
test_error = mean(df.pred==test_set$Direction)
test_error
```
## Then using LDA model to predict the Direction using the same data 
```{r}
## the lac() will provide class as the predicted results
library(MASS)
lda_fit = lda(Direction~.,data = train_set)
lda_prob = predict(lda_fit,test_set)
table(lda_prob$class,test_set$Direction)
test_error_lda = mean(lda_prob$class==test_set$Direction)
test_error_lda
```
## Then using QDA model to predict the Direction using the same data
```{r}
qda_fit = qda(Direction~.,data = train_set)
qda_prob = predict(qda_fit,test_set)
table(qda_prob$class,test_set$Direction)
test_error_qda = mean(qda_prob$class==test_set$Direction)
test_error_qda
```
##Conclusion 
# 1.When the real classification boundary is linear, LR and LDA usually perform better; when the real classification boundary is # generally nonlinear, QDA usually performs better
# 2.Both LR and LDA will produce linear classification boundaries. The only difference between the two is that the coefficients  # of LR are obtained by calculating MSE, while the coefficients of LDA are calculated using the estimated values of the mean and #variance of the normal distribution; LR is suitable for two classification problems. , For multi-class problems, LDA is more #common
#3.When the sample can be completely linearly classified, the LR parameter estimation will be unstable, and the LR method is not # applicable at this time
#4. LDA model needs the features share the same variance but QDA does not.