---
title: "Regression Tree & Classification Tree"
author: "YUANXU"
date: "10/23/2020"
output: html_document
---
```{r}
library(ISLR)
library(tree)
```
## Classification Tree
## Using OJ(orange juice data),split the data into training set and test set, this time we use real numbers not percentage
```{r}
attach(OJ)
dim(OJ)
set.seed(1)
subset = sample(1:nrow(OJ),800)
OJ.train = OJ[subset,]
OJ.test = OJ[-subset,]
dim(OJ.train)
```
## Build a tree model based on the training set the tree package will automatically pick the impoartant indicators
```{r}
tree.OJ = tree(Purchase~.,data = OJ.train)
summary(tree.OJ)
```
##List the details of the tree and plot the tree
```{r}
tree.OJ
plot(tree.OJ)
text(tree.OJ)
```
##Predict the tree model with test data and build a confusion matrix and calculate the testerror
```{r}
tree.pred = predict(tree.OJ,OJ.test,type="class")
table(tree.pred,OJ.test$Purchase)
testeeror = 1-mean(tree.pred==OJ.test$Purchase)
testeeror
```
## Using cross validation method to prune the tree and plot the MSE with K 
```{r}
cv.OJ = cv.tree(tree.OJ,FUN=prune.misclass)
plot(cv.OJ$size,cv.OJ$dev,type = "b",xlab="Tree Size", ylab = "Dev")

```
##Using the best tree size and build a new tree model 
```{r}
prune.OJ=prune.misclass(tree.OJ,best=8)
plot(prune.OJ)
text(prune.OJ)

```
##Making new prediction
```{r}
tree.pred2=predict(prune.OJ,OJ.test,type="class")
table(tree.pred2,OJ.test$Purchase)
testerror2 = 1-mean(tree.pred2==OJ.test$Purchase)
testerror2
```
## Then using Carseats data to build regression tree model for the Sales value
```{r}
fix(Carseats)
set.seed(1)
subset=sample(1:nrow(Carseats),200,replace = FALSE)
Carseats_train=Carseats[subset,]
Carseats_test=Carseats[-subset,]
dim(Carseats_train)
```
##The tree package will automatically make regression tree or classification tree depends on the target value. 
##If the target value is blooean type it will build classification tree and if the target value is numerical it will build regression tree.
```{r}
tree.Carseats=tree(Sales~.,data=Carseats_train)
summary(tree.Carseats)

```
```{r}
plot(tree.Carseats)
text(tree.Carseats,pretty = 0)
```
```{r}
tree.pred=predict(tree.Carseats,Carseats_test)
testerror = mean((tree.pred-Carseats_test$Sales)^2)
testerror
```
##Using cross validation method to build a new regression tree model by changing the tree size
```{r}
cv.Carseats=cv.tree(tree.Carseats)
names(cv.Carseats)
plot(cv.Carseats$size,cv.Carseats$dev,type="b",xlab = "Tree size", ylab = "Deviance")

```
```{r}
prune.Carseats=prune.tree(tree.Carseats,best=16)
tree.pred1=predict(prune.Carseats,Carseats_test)
testerror1 = mean((tree.pred1-Carseats_test$Sales)^2)
testerror1
```
